### 2014-10-31 simulation.Rmd

>>>>

# Pairwise marginal posteriors from MCMC, colored by time in MCMC run
```{r, results="asis"}
mcmcrun <- model@results$batch
subseq <- seq(1,nrow(mcmcrun),length.out=1000)
x <- rbind( mcmcrun[subseq,], mr_compare$simulated ) 
# color by time
cols <- c( adjustcolor(rainbow(64),.2)[1+floor(65*(1:(nrow(x)-1))/nrow(x))], adjustcolor("black",.5) )
pairs( x, col=cols, pch=20, cex=c(rep(.5,nrow(x)-1),2) )
```
